% LaTeX file for resume

\documentclass[line,margin]{cv}

\usepackage[usenames,dvipsnames]{color}
% margin control
\usepackage{scrextend}

% hyperlinks
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	urlcolor=Black,
	urlbordercolor={0 0 0}
}

% line spacing
\usepackage{setspace}
\linespread{1.3}

% for compact itemization
\usepackage{enumitem}
\setlist{nolistsep}
\setlength{\itemsep}{-.08ex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%% My settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% page margin
\addtolength{\textwidth }{50pt}
\addtolength{\oddsidemargin }{-30pt}

% set paragraph margin (spacing)
\setlength{\parskip}{1.5ex plus 0.3ex minus 0.3ex}

% linespread
\linespread{1.1}

% Indented block
\newenvironment{block}
{
	\begin{addmargin}[2em]{0em}% 2em left, 0em right
}
{
	\end{addmargin}
}

% Section font becomes Small Capitals
\renewcommand{\sectionfont}{\scshape}

\newcommand{\myemph}{\textbf}

% Use a smaller bullet for listing
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

% links
\newcommand{\SUNY}{\href{http://www.stonybrook.edu/}{State University of New York at Stony Brook}}
\newcommand{\Google}{\href{https://www.google.com/}{Google}}
\newcommand{\GoogleBrain}{\href{http://research.google.com/teams/brain/}{Google Brain}}
\newcommand{\Facebook}{\href{https://www.facebook.com/}{Facebook}}
\newcommand{\SUNYSchool}{\href{www.cs.stonybrook.edu}{Computer Science Department}}
\newcommand{\Fudan}{\href{http://www.fudan.edu.cn/englishnew/}{Fudan University}}
\newcommand{\FudanSchool}{\href{http://www.cs.fudan.edu.cn/}{School of Computer Science}}
\newcommand{\MyMail}{\href{mailto:alan.yt.tian@gmail.com}{alan.yt.tian@gmail.com}}
\newcommand{\MSRA}{\href{http://research.microsoft.com/en-us/labs/asia/default.aspx}{Microsoft Research Asia}}
\newcommand{\DMAS}{\href{http://research.microsoft.com/en-us/groups/dmas/}{Data Management, Analytics and Services Group}}
\newcommand{\Haixun}{\href{http://haixun.olidu.com/}{Dr.\ Haixun Wang}}
\newcommand{\WSM}{\href{http://research.microsoft.com/en-us/groups/wsm/}{Web Search and Mining Group}}
\newcommand{\Zhongyuan}{\href{http://www.wangzhongyuan.com/}{Dr.\ Zhongyuan Wang}}
\newcommand{\Skiena}{\href{https://www3.cs.stonybrook.edu/~skiena/}{Prof.\ Steven Skiena}}
\newcommand{\GDM}{\href{http://gdm.fudan.edu.cn}{Graph Data Management Lab}}
\newcommand{\Yanghua}{\href{http://gdm.fudan.edu.cn/GDMWiki/Wiki.jsp?page=Yanghuaxiao}{Prof.\ Yanghua Xiao}}
\newcommand{\sgouws}{\href{http://research.google.com/pubs/StephanGouws.html}{Dr.\ Stephan Gouws}}
\newcommand{\jesseengel}{\href{https://ai.google/research/people/JesseEngel}{Dr.\ Jesse Engel}}
\newcommand{\ICPC}{\href{http://icpc.baylor.edu/}{ACM-ICPC}}
\newcommand{\Codejam}{\href{http://code.google.com/codejam/}{Google Code Jam}}


% compact itemize
\newenvironment{citemize}
{ \begin{itemize}[itemsep=-0.4ex] }
{ \end{itemize} }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%% Real staffs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\name{Yingtao Tian}

\address{\textit{E-mail:} \MyMail}

\begin{resume}

\section{Education}

	{\bf \SUNY}, New York, U.S. \hfill 2014 - 2019
	\begin{block}
		Ph.D, Computer Science. Advisor: \Skiena
	\end{block}

	{\bf \Fudan}, Shanghai, China. \hfill 2010 - 2014

	\begin{block}
		B.Sc., Computer Science and Technology 
	\end{block}

\section{Experience}

	{\bf \GoogleBrain}, Tokyo, Japan. {\itshape Research Software Engineer} \hfill Summer 2019 - Now
	\begin{block}
		Research on generative models and more.
	\end{block}

	{\bf \GoogleBrain}, California, U.S. {\itshape Software Engineering Intern} \hfill Summer 2018
	\begin{block}
		Research on the latent space of generative models. Hosted by \jesseengel
	\end{block}

	{\bf \Facebook}, California, U.S. {\itshape Software Engineering Intern} \hfill Summer 2017
	\begin{block}
		Research on natural language understanding. Hosted by \Haixun
	\end{block}

	{\bf \GoogleBrain}, California, U.S. {\itshape Software Engineering Intern} \hfill Summer - Fall 2016
	\begin{block}
		Research on representation learning. Hosted by \sgouws
	\end{block}

	{\bf \Google}, New York, United States {\itshape Software Engineering Intern} \hfill Summer 2015
	\begin{block}
		User-generated activity profiling and analysis. Hosted by Dr.\ Xiaomeng Ban
	\end{block}

	{\bf \MSRA}, Beijing, China. {\itshape Research Intern} \hfill 2013

	\begin{block}
		Learning representation from large knowledge base. Hosted by: \Haixun

		Concept level semantic analysis. Hosted by \Zhongyuan
	\end{block}

	{\bf \Fudan}, Shanghai, China. {\itshape Research Assistant} \hfill Fall 2012
	\begin{block}
		Large scale information extract from crawled web pages. Advised by \Yanghua
	\end{block}


\section{Publications / Working Papers}
	{\bf  KaoKore: A Pre-modern Japanese Art Facial Expression Dataset}
	\emph{Yingtao Tian}, Chikahiko Suzuki, Tarin Clanuwat, Mikel Bober-Irizar, Alex Lamb, Asanobu Kitamoto\\
	\emph{To Appear in the Proceedings of the Eleventh International Conference on Computational Creativity, ICCC'20}

	{\bf  A Transfer-Learnable Natural Language Interface for Databases}
	Wenlu Wang, \emph{Yingtao Tian}, Haixun Wang, Wei-Shinn Ku\\
	\emph{In the Proceedings of the IEEE International Conference on Data Engineering (ICDE) 2020}
	
	{\bf  Learning to Represent Bilingual Dictionaries}
	Muhao Chen*, \emph{Yingtao Tian}*, Haochen Chen, Kai-Wei Chang, Steven Skiena, Carlo Zaniolo  (* Equal Contribution)\\
	\emph{In the Proceedings of the IEEE International Conference on Data Engineering (ICDE) 2020}
	
	{\bf  Enhanced Network Embeddings via Exploiting Edge Attributes}
	 Haochen Chen, Xiaofei Sun, \emph{Yingtao Tian}, Muhao Chen, Bryan Perozzi and Steven Skiena\\
	\emph{In Proceedings of the International Conference on Information and Knowledge Management (CIKM) 2018}

	{\bf Social Relation Inference via Label Propagation}
	\emph{Yingtao Tian}, Haochen Chen, Bryan Perozzi, Muhao Chen, Xiaofei Sun and Steven Skiena\\
	\emph{In the proceeding of the 41st European Conference on Information Retrieval (ECIR 2019)}
	
	{\bf DeepAnnotator: Genome Annotation with Deep Learning,}
	Mohammad Ruhul Amin, Alisa Yurovsky, \emph{Yingtao Tian}, Steven Skiena \\
	\emph{In Proceedings of the 9th ACM Conference on Bioinformatics, Computational Biology, and Health Informatics (ACM BCB-2018)}
	
	{\bf Simple Neologism Based Domain Independent Models to Predict Year of Authorship}
	 Vivek Kulkarni, \emph{Yingtao Tian}, Parth Dandiwala, Steven Skiena \\
	\emph{In Proceedings of the 27th International Conference on Computational Linguistics (COLING 2018)}

	{\bf Co-training Embeddings of Knowledge Graphs and Entity Descriptions for Cross-lingual Entity Alignment}
	Muhao Chen, \emph{Yingtao Tian}, Kai-Wei Chang, Steven Skiena, Carlo Zaniolo\\
	\emph{In Proceedings of the 27th International Joint Conference on Artificial Intelligence (IJCAI), IJCAI/AAAI Press 2018.}
	
    {\bf Syntax-Directed Variational Autoencoder for Structured Data}
    Hanjun Dai*, \emph{Yingtao Tian}* , Bo Dai , Steven Skiena, Le Song (* Equal Contribution)\\
    \emph{In Proceedings of the International Conference on Learning Representations (ICLR), 2018. \\
    Best Paper Award, NIPS 2017 workshop for Machine Learning for Molecules and Materials.}
    
	{\bf Embedding-based Relation Prediction for Ontology Population}
	Muhao Chen, \emph{Yingtao Tian}, Xuelu Chen, Zijun Xue, Carlo Zaniolo\\
	\emph{In Proceedings of the 17th SIAM International Conference on Data Mining (SDM), SIAM 2018.}

    {\bf Towards End-End Generation of High-Resolution Images with Generative Adversarial Networks}
    \href{http://make.girls.moe/#/}{[Online Demo]}
    Yanghua Jin, Jiakai Zhang, Minjun Li, \emph{Yingtao Tian}, Huachun Zhu\\
    \emph{Accepted and presented in spotlight, NIPS 2017 workshop for Machine Learning for Creativity and Design.}

    {\bf Multilingual Knowledge Graph Embeddings for Cross-lingual Knowledge Alignment}
    Muhao Chen, \emph{Yingtao Tian}, Mohan Yang, Carlo Zaniolo.\\
    \emph{In Proceedings of the 26th International Joint Conference on Artificial Intelligence (IJCAI), IJCAI/AAAI Press 2017.}

\section{Professional Services }
	Reviewer, \emph{LREC 2018, COLING 2016}

\section{Honors and Awards}
	\myemph{27th place}, 35th Annual World Final of the \ICPC \,, 2011

	\myemph{Gold Medal}, \ICPC\ Asia Chengdu Regional Contest, 2011

	\myemph{Championship and Gold medal}, \ICPC\ Asia Amritapri Regional Contest, 2010

\section{Services}
    Assistant coach, \ICPC\ team of Fudan University \hfill 2010 - 2013

    Main technical staff, \ICPC\ Shanghai Site Contest \hfill Oct.\ 2011

\end{resume}
\end{document}
