% LaTeX file for resume

\documentclass[line,margin]{cv}

\usepackage{comment}

\usepackage[usenames,dvipsnames]{color}
% margin control
\usepackage{scrextend}


\usepackage{xhfill}


% hyperlinks
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=Blue,
  urlbordercolor={0 0 0}
}

% line spacing
\usepackage{setspace}
\linespread{1.2}

% for compact itemization
\usepackage{enumitem}
\setlist{nolistsep}
\setlength{\itemsep}{-.08ex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%% My settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% page margin
\addtolength{\textwidth }{50pt}
\addtolength{\oddsidemargin }{-30pt}

% set paragraph margin (spacing)
\setlength{\parskip}{1.5ex plus 0.3ex minus 0.3ex}

% linespread
\linespread{1.1}

% Indented block
\newenvironment{block}
{
  \begin{addmargin}[2em]{0em}% 2em left, 0em right
}
{
  \end{addmargin}
}

% Section font becomes Small Capitals
\renewcommand{\sectionfont}{\scshape}

\newcommand{\myemph}{\textbf}

% change hrulefill thickness, which is used below
\renewcommand{\hrulefill}{%
  \leavevmode\leaders\hrule height 1pt\hfill\kern0pt }

% pub list header. see https://tex.stackexchange.com/questions/15119/draw-horizontal-line-left-and-right-of-some-text-a-single-line
\newcommand*\ruleline[1]{\par\noindent\raisebox{.8ex}{\makebox[\linewidth]{\hrulefill\hspace{1ex}\raisebox{-.8ex}{#1}\hspace{1ex}\hrulefill}}}

% Use a smaller bullet for listing
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

% links
\newcommand{\SUNY}{\href{http://www.stonybrook.edu/}{State University of New York at Stony Brook}}
\newcommand{\Google}{\href{https://www.google.com/}{Google}}
\newcommand{\GoogleBrain}{\href{http://research.google.com/teams/brain/}{Google Brain}}
\newcommand{\GoogleDeepMind}{\href{https://www.deepmind.com/}{Google DeepMind}}
\newcommand{\Facebook}{\href{https://www.facebook.com/}{Facebook}}
\newcommand{\SUNYSchool}{\href{www.cs.stonybrook.edu}{Computer Science Department}}
\newcommand{\Fudan}{\href{http://www.fudan.edu.cn/englishnew/}{Fudan University}}
\newcommand{\FudanSchool}{\href{http://www.cs.fudan.edu.cn/}{School of Computer Science}}
\newcommand{\MyWebsite}{\href{https://alantian.net}{alantian.net}}
\newcommand{\MyMail}{\href{mailto:alan.yt.tian@gmail.com}{\nolinkurl{alan.yt.tian@gmail.com}}}
\newcommand{\MSRA}{\href{http://research.microsoft.com/en-us/labs/asia/default.aspx}{Microsoft Research Asia}}
\newcommand{\DMAS}{\href{http://research.microsoft.com/en-us/groups/dmas/}{Data Management, Analytics and Services Group}}
\newcommand{\Haixun}{\href{http://haixun.olidu.com/}{Dr.\ Haixun Wang}}
\newcommand{\WSM}{\href{http://research.microsoft.com/en-us/groups/wsm/}{Web Search and Mining Group}}
\newcommand{\Zhongyuan}{\href{http://www.wangzhongyuan.com/}{Dr.\ Zhongyuan Wang}}
\newcommand{\Xiaomeng}{\href{https://www.linkedin.com/in/xiaomengban/}{Dr.\ Xiaomeng Ban}}
\newcommand{\Skiena}{\href{https://www3.cs.stonybrook.edu/~skiena/}{Prof.\ Steven Skiena}}
\newcommand{\GDM}{\href{http://gdm.fudan.edu.cn}{Graph Data Management Lab}}
\newcommand{\Yanghua}{\href{http://gdm.fudan.edu.cn/GDMWiki/Wiki.jsp?page=Yanghuaxiao}{Prof.\ Yanghua Xiao}}
\newcommand{\sgouws}{\href{http://research.google.com/pubs/StephanGouws.html}{Dr.\ Stephan Gouws}}
\newcommand{\jesseengel}{\href{https://ai.google/research/people/JesseEngel}{Dr.\ Jesse Engel}}
\newcommand{\ICPC}{\href{http://https://icpc.global//}{ACM-ICPC}}
\newcommand{\Codejam}{\href{http://code.google.com/codejam/}{Google Code Jam}}


% compact itemize
\newenvironment{citemize}
{ \begin{itemize}[itemsep=-0.4ex] }
{ \end{itemize} }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%% Real staffs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\name{Yingtao Tian}

\address{Research Scientist \textbullet{} \GoogleDeepMind{}  / \MyMail{} / \MyWebsite}

\begin{resume}

\section{Research Interests}

  I am excited at combining \textbf{computational approach}, with artists, culture, humanities and designer's consideration.
  I propose techniques and tools that have both \textbf{addressed the needs in creative settings} and \textbf{improved the core machine learning}. 
  Leading collaborations with internal and external stake-holders.
  More details in my \href{https://alantian.net/research_statement.pdf}{research statement}.

\section{Research / Industry Experience}

  {\bf \GoogleDeepMind{} (formerly \GoogleBrain)} {Research Scientist} \hfill 2019 - Present
    \begin{itemize}
      \item \textbf{Generating artifacts with artistical discretion.}
        \begin{itemize}
          \item Proposed novel models for abstract art, multiple text prompts and collective intelligence.
        \end{itemize}
      \item\textbf{Machine learning-boosted tools for historical and cultural works.}
        \begin{itemize}
          \item Pioneered in making ML-ready dateset for pre-modern japanese artworks / longest consecutive typhoon satellite image.
          \item Proposed ML-based historical figure analysis / calligraphy generation for CJK characters.
        \end{itemize}
      \item \textbf{Advancing Machine Learning Techniques in Black-Box Optimization.}
        \begin{itemize}
          \item Pioneered in fitting evolution strategy, an black-box optimization, to modern settings.
          \item Proposing fundation models (LLMs and transformers) based approaches to black-box optimizations.
        \end{itemize}
    \end{itemize}

  {\bf Internships} \GoogleBrain{},  \Facebook{}, \Google{}, \MSRA{} \hfill Periodically 2013 - 2018
    \begin{itemize}
      \item Proposed latent space transfer for multi-modality tasks.
      \item Implemented natural language interface to database system.
    \end{itemize}


\section{Major Publications}

  \ruleline{\textbf{Generating Artifacts with Artistical Discretion}}

  {
  \small
  \href{https://arxiv.org/abs/2109.08857}{Modern Evolution Strategies for Creativity: Fitting Concrete Images and Abstract Concepts}.
  \textbf{Yingtao Tian}, David Ha.
  \emph{Proceedings of EvoMUSART 2022}

  \href{https://arxiv.org/abs/2204.08472}{Simultaneous Multiple-Prompt Guided Generation Using Differentiable Optimal Transport}.
  \textbf{Yingtao Tian}, David Ha, Marco Cuturi. \emph{Proceeding of ICCC 2022}

  \href{https://direct.mit.edu/isal/proceedings-pdf/isal/35/112/2149148/isal_a_00676.pdf}{Evolving Collective AI: Simulation of Ants Communicating via Chemicals}.
  Ryosuke Takata, Yujin Tang, \textbf{Yingtao Tian}, Norihiro Maruyama, Hiroki Kojima, Takashi Ikegami. 
  \emph{The 2023 Conference on Artificial Life}
  }

  \ruleline{\textbf{Machine learning-Boosted Tools for Historical and Cultural works}}

  {
  \small
  \href{https://arxiv.org/abs/2002.08595}{KaoKore: A Pre-modern Japanese Art Facial Expression Dataset}.
  \textbf{Yingtao Tian}, Chikahiko Suzuki, Tarin Clanuwat, Mikel Bober-Irizar, Alex Lamb, Asanobu Kitamoto. 
  \emph{Proceeding of ICCC 2020}

  \href{https://arxiv.org/abs/2106.02267}{Ukiyo-e Analysis and Creativity with Attribute and Geometry Annotation}.
  \textbf{Yingtao Tian}, Tarin Clanuwat, Chikahiko Suzuki, Asanobu Kitamoto. 
  \emph{Proceeding of ICCC 2021}

  \href{https://aclanthology.org/2023.emnlp-main.266/}{MingOfficial: A Ming Official Career Dataset and a Historical Context-Aware Representation Learning Framework}
  You-Jun Chen, Hsin-Yi Hsieh, Yu Tung Lin, \textbf{Yingtao Tian}, Bert Chan, Yu-Sin Liu, Yi-Hsuan Lin, Richard Tzong-Han Tsai. 
  \emph{Proceeding of EMNLP 2023}

  \href{https://arxiv.org/abs/2311.02665}{Digital Typhoon: Long-term Satellite Image Dataset for the Spatio-Temporal Modeling of Tropical Cyclones}.
  Asanobu Kitamoto, Jared Hwang, Bastien Vuillod, Lucas Gautier, \textbf{Yingtao Tian}, Tarin Clanuwat. 
  \emph{Proceeding of NeurIPS 2023 Systems Datasets and Benchmarks Track}

  \href{https://arxiv.org/abs/2404.05212}{DiffCJK: Conditional Diffusion Model for High-Quality and Wide-coverage CJK Character Generation}.
  \textbf{Yingtao Tian} \emph{Proceeding of ICCC 2024}
  }

  \ruleline{\textbf{Advancing Machine Learning Techniques in Black-Box Optimization}}

  {
  \small
  \href{https://arxiv.org/abs/2202.05008}{EvoJAX: Hardware-Accelerated Neuroevolution}
  Yujin Tang, \textbf{Yingtao Tian}, David Ha.   \emph{Proceeding of GECCO 2022}

  \href{https://openreview.net/forum?id=s6qtLyR6uJ}{NeuroEvoBench: Benchmarking Neuroevolution for Large-Scale Machine Learning Applications}.
  Robert Tjarko Lange, Yujin Tang, \emph{Yingtao Tian}. \emph{Proceeding of NeurIPS 2023 Systems Datasets and Benchmarks Track}

  \href{https://arxiv.org/abs/2304.10770}{DEIR: Efficient and Robust Exploration through Discriminative-Model-Based Episodic Intrinsic Rewards}.
  Shanchuan Wan, Yujin Tang, \textbf{Yingtao Tian}, Tomoyuki Kaneko. \emph{IProceeding of IJCAI 2023}

  \href{https://arxiv.org/abs/2402.18381}{Large Language Models As Evolution Strategies}.
  Robert Tjarko Lange, \textbf{Yingtao Tian}, Yujin Tang. \emph{Proceeding of GECCO 2024}

  \href{https://arxiv.org/abs/2403.02985}{Evolution Transformer: In-Context Evolutionary Optimization}.
  Robert Tjarko Lange, \textbf{Yingtao Tian}, Yujin Tang. \emph{Proceeding of GECCO 2024}

  \href{https://arxiv.org/abs/2403.02985}{Position Paper: Leveraging Fuoundational Models for Black-Box Optimization: Benefits, Challenges, and Future Directions}.
  Xingyou Song, \textbf{Yingtao Tian}, Robert Tjarko Lange, Chansoo Lee, Yujin Tang, Yutian Chen \emph{Proceeding of ICML 2024}
  }

  \ruleline{\textbf{Representation Learning for Data in Multiple Modalities}}

  {
  \small
  \href{https://arxiv.org/abs/1808.03726}{Learning to Represent Bilingual Dictionaries}.
  Muhao Chen*, \textbf{Yingtao Tian*}, Haochen Chen, Kai-Wei Chang, Steven Skiena, Carlo Zaniolo. \emph{In the Proceedings of the SIGNLL Conference on Computational Natural Language Learning (CoNLL) 2019}

  \href{http://www.mlgworkshop.org/2018/papers/MLG2018_paper_58.pdf}{Social Relation Inference via Label Propagation}.
  \textbf{Yingtao Tian*}, Haochen Chen, Bryan Perozzi, Muhao Chen, Xiaofei Sun, Steven Skiena. \emph{In the proceeding of the 41st European Conference on Information Retrieval (ECIR 2019)}

  \href{http://www.mlgworkshop.org/2018/papers/MLG2018_paper_58.pdf}{Syntax-Directed Variational Autoencoder for Structured Data}.
  Hanjun Dai*, \textbf{Yingtao Tian*}, Bo Dai, Steven Skiena, Le Song. \emph{In Proceedings of the International Conference on Learning Representations (ICLR) 2018}
  }

  \hrulefill


\section{Education}

  {\bf \SUNY}, New York, U.S. \hfill 2014 - 2019
  \begin{block}
    Ph.D, Computer Science. Advisor: \Skiena{} \\
    Thesis: Representation Learning-based Approaches for Modeling Data in Multiple Modalities
  \end{block}

  {\bf \Fudan}, Shanghai, China. \hfill 2010 - 2014

  \begin{block}
    B.Sc., Computer Science and Technology 
  \end{block}


\section{Awards}
  \myemph{27th place}, 35th Annual World Final of the \ICPC \,, 2011

  \myemph{Gold Medal}, \ICPC\ Asia Chengdu Regional Contest, 2011

  \myemph{Championship and Gold medal}, \ICPC\ Asia Amritapri Regional Contest, 2010

\end{resume}
\end{document}
